Directly inferring Distances and Physical Properties of Stellar Systems with Simulation Based Inference

### 2023-12-13 src/tex/ms.tex
[showyourwork] overleaf sync

% Title
\title{Directly inferring Distances and Physical Properties of stellar system using Simulation Based Inference}

@@

\section{Inference on a Mock Galaxy}
\label{sec:self-test}
\begin{figure*}
    \centering
    \includegraphics[width = 0.8\textwidth]{figures/self_test_post_corner.pdf}
    \includegraphics[width = 0.8\textwidth]{figures/self_test_ims.pdf}
    \caption{Plotting the results of a simple injection-recovery test. Seems to be pretty good although it is a little too confident about the stellar population parameters}
    \script{plot_self_test.ipynb}
    \label{fig:self_test_post}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width = 0.95\columnwidth]{figures/self_test_sbc.pdf}
    \caption{Plotting the results of a simple injection-recovery test. Seems to be pretty good although it is a little too confident about the stellar population parameters}
    \script{plot_self_test.ipynb}
    \label{fig:self_test_sbc}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/Pal4_post_corner.pdf}
    \includegraphics[width=0.45\textwidth]{figures/Pal13_post_corner.pdf}
    \includegraphics[width=0.4\textwidth]{figures/Pal4_ims_post.pdf}
    \hspace{1cm}
    \includegraphics[width=0.4\textwidth]{figures/Pal13_ims_post.pdf}
    \caption{Caption}
    \script{plot_gc.py}
    \label{fig:GCs}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/ESO_294_10_post_corner.pdf}
    \includegraphics[width=0.3\textwidth]{figures/ESO_294_10_ims_post.pdf}
    \includegraphics[width=0.5\textwidth]{figures/ESO_410_05_post_corner.pdf}
    \includegraphics[width=0.3\textwidth]{figures/ESO_410_05_ims_post.pdf}
    \caption{Caption}
    \script{plot_scul_dw.ipynb}
    \label{fig:sdw_2mpc}
\end{figure*}

>>>>

% Title
\title{Directly inferring Distances and Physical Properties of Stellar Systems with Simulation Based Inference}

@@

\section{Inference on a Mock Galaxy}
\label{sec:self-test}
\begin{figure*}
    \centering
    \includegraphics[width = 0.9\textwidth]{figures/self_test_ims.pdf}
    \includegraphics[width = 0.75\textwidth]{figures/self_test_post_corner.pdf}
    \caption{Plotting the results of an injection-recovery test. Seems to be pretty good although it is a little too confident about the stellar population parameters}
    \script{plot_self_test.ipynb}
    \label{fig:self_test_post}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width = 0.95\columnwidth]{figures/self_test_sbc.pdf}
    \caption{Simulation based calibration (SBC). In short you want the distribution of ranks to be uniform within the grey line, which we are more are less so passed this basic check.}
    \script{plot_self_test.ipynb}
    \label{fig:self_test_sbc}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/Pal4_post_corner.pdf}
    \includegraphics[width=0.45\textwidth]{figures/Pal13_post_corner.pdf}
    \includegraphics[width=0.4\textwidth]{figures/Pal4_ims_post.pdf}
    \hspace{1cm}
    \includegraphics[width=0.4\textwidth]{figures/Pal13_ims_post.pdf}
    \caption{Inference on the globular clusters Pal4 and Pal13. Both are qualitatively correct, Pal4 at $\sim$ 100 kpc and Pal13 at $\sim$ 27 kpc. Pal 4 looks pretty good its thought to be a tad younger than 10Gyr from what I read so in good agreement. Pal 13 looks a little off, the images don't line up exactly and the inferred age is too young. From reading this cluster is known to have a large population of blue stragglers (Binary interactions that extend the main sequence). This probably breaks the isochrones as binary interactions are not in MIST. But the distance is more or less right so that's encouraging.}
    \script{plot_gc.py}
    \label{fig:GCs}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/ESO_294_10_post_corner.pdf}
    \includegraphics[width=0.3\textwidth]{figures/ESO_294_10_ims_post.pdf}
    \includegraphics[width=0.5\textwidth]{figures/ESO_410_05_post_corner.pdf}
    \includegraphics[width=0.3\textwidth]{figures/ESO_410_05_ims_post.pdf}
    \caption{Inference on two galaxies in the sculptor group, ESO 294-010 on top and ESO 410-005 on the bottom. In general really good agreement with other measurements and the images from the posterior, by eye, look a lot like the observed images. I'm not sure whether to include the stellar masses. We are biased a little low but that could be chocked up to some normalization issues that we should look into.}
    \script{plot_scul_dw.ipynb}
    \label{fig:sdw_2mpc}
\end{figure*}
